### 2013-02-16 doc/icml2013/algo.tex
edit

%Define $\sM_p = \{ \sum_{h=1}^k \pi_h \beta_h\tp{p} : \pi_h \in \R^k, \beta_h
%\in \R^d \}$ be the set of all $p$-th order compound parameters.
%Let $\bM_p$ be the set of

%Define the symmetric rank
%\begin{align}
%\E[\cvec(x\tp{p})\tp{2}] \succ 0.
%\end{align}

In this section, we conduct a theoretical analysis of Spectral Experts.
In particular, we prove that it enjoys consistent parameter estimates.
\begin{theorem}[Convergence of Spectral Experts]
  \label{thm:convergence}
Each dataset $\sD_p$ (for $p = 1, 2, 3$) consists of $n$ i.i.d. points drawn from the mixture
of linear regressions model with parameter $\theta^*$
(having three independent copies simplifies the analysis).
Assume that $\E[\cvec(x\tp{p})\tp{2}] \succ 0$ for each $p \in \{1,2,3\}$
and that $d \ge k$.
Let $\|x\|_2 \le R$ with probability $1$
and let $\|\beta_h\|_2 \le L$ for all $h \in [k]$.
Suppose the number of samples is
$n = \Omega(d^p R^p \sigmamin(\Sigma_p)^{-1} \sqrt{p \log(d) \log(1/\delta)})$ and
$n = \Omega\left( \sigma^6 L^6 R^12 k \sigmamin(\Sigma_p)^{-2} \frac{\log^3 (1/\delta)}{\epsilon^2} \right)$,
and that the regularization strengths $\lambda_n^{(2)}$ and $\lambda_n^{(3)}$ are
$\Omega(\sigma^3 L^3 R^6 \sqrt{\frac{\log(1/\delta)}{n}})$,
then the parameter estimates $\hat\theta$ returned by
\algorithmref{algo:spectral-experts} (with the columns appropriate permuted)
satisfies 
$\|\hat\pi - \pi^*\|_{\infty} \le \epsilon$
and for all $h \in [k]$,
$\|\hat\beta_h - \beta^*_h\|_2 \le \frac{\epsilon}{\pi_h^*}$.
\end{theorem}

>>>>

In this section, we provide theoretical guarantees for our Spectral Experts algorithm.
In particular, the following theorem provides a rate of convergence:

\begin{theorem}[Convergence of Spectral Experts]
  \label{thm:convergence}
Each dataset $\sD_p$ (for $p = 1, 2, 3$) consists of $n$ i.i.d. points drawn from the mixture
of linear regressions model with parameter $\theta^*$
(having three independent copies simplifies the analysis).
Let $\|x\|_2 \le R$ with probability $1$
and let $\|\beta_h\|_2 \le L$ for all $h \in [k]$.
Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$, 
and assume $\Sigma_p \succ 0$ for each $p \in \{1,2,3\}$.
Assume $d \ge k$.
Suppose the number of samples is
$n = \Omega(d^p R^p \sigmamin(\Sigma_p)^{-1} \sqrt{p \log(d) \log(1/\delta)})$ and
$n = \Omega\left( \sigma^6 L^6 R^12 k \sigmamin(\Sigma_p)^{-2} \frac{\log^3 (1/\delta)}{\epsilon^2} \right)$,
and that the regularization strengths $\lambda_n^{(2)}$ and $\lambda_n^{(3)}$ are
$\Omega(\sigma^3 L^3 R^6 \sqrt{\frac{\log(1/\delta)}{n}})$,
then the parameter estimates $\hat\theta$ returned by
\algorithmref{algo:spectral-experts} (with the columns appropriate permuted)
satisfies 
$\|\hat\pi - \pi^*\|_{\infty} \le \epsilon$
and for all $h \in [k]$,
$\|\hat\beta_h - \beta^*_h\|_2 \le \frac{\epsilon}{\pi_h^*}$.
\end{theorem}
